### 2013-09-04 Tex/chapters/results.tex
Containment Theorem

    temperature than the GG. Also \(T_c\) of the RNG decreases

@@

    \subsubsection{Influence of the Average Degree on the Critical Temperature}
        One basic property of a graph is its average degree \(K\) -- sometimes
        called average \emph{coordination number}. \(K\) is defined as the mean count
        of neighbors per node.
            K = \frac{1}{N} \sum_{\avg{i,j}} 1.
            \label{eq:degree}
        It is well known that the degree has an impact on the critical temperature.
        For example the Honeycomb lattice is of degree \(K=3\) and the
        respective critical temperature can be obtained by analytic means \cite{Wannier1945},
        yielding
            \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52.
            \label{eq:exactHCTc}
        Note that this is lower than the critical temperature \(T_c = 2.269...\)
        characteristic for the square lattice with degree \(K=4\).\\
        This is plausible, because more edges lead to more neighbors.
        Consider, e.g., a fully polarized spin configuration. Now, the
        energy needed to flip a spin so that it assumes an orientation opposite
        to the orientation of its neighbors increases with the number of
        its neighbors. So the more edges are in
        the graph the more stable the system becomes with respect to spin flips
        at low \(T\), leading to an increasing value of \(T_c\).
        This is also an explanation why the \(T_c\) of the RNG is always
        lower than that of the GG: The degree of the RNG is lower.\\
        If one plots the degree of the graphs at different \(\sigma\) like
        in Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
        one recognizes that \(T_c\) and \(K\) are evidently correlated.
        The values for \(K\) are obtained as an average over \(100\)
        realizations of each graph type for \(L=16\) and \(L=32\) lattices.
        %~ Note that \(K\) is independent of \(L\) because of the periodic boundary.
        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        one can see that these curves are almost identical and the small
        errorbars suggest that they are sufficiently precise for this purpose.
        It seems reasonable to normalize \(T_c\) by the degree of the underlying
        graph. This is done in Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
        Indeed the normalization eliminates the jump and reduces the
        slope of the \(T_c\) curve for the GG. Hence it reduces differences
        between the RNG and the GG. However the elimination of the jump is
        unfortunately a coincidence and probably caused by a lucky choice of the
        function, which determines the coupling constants \(J\). As proof for
        this claim in Sec.\ \ref{appendix:fixedCoupling} the same analysis
        is performed for a model with fixed \(J\). There the jump gets narrower
        but is still existent. Anyway, the degree seems to have an impact on
        the critical temperature \(T_c\), but it is not a trivial one.
        Note that even after the normalization, the values of \(T_c / K\)
        for the RNG are smaller than those for the GG.
                \label{sfig:deg:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
                \label{sfig:deg:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_deg}

@@

            \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
            {
                Top: Critical Temperature \(T_c\) of the graph over different
                disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.\\
                Bottom: Critical temperatures normalized by degree \(K\) over
                different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
                are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
                from Sec.\ \ref{sssec:J}.
            }
            \label{fig:Tc_deg_A0}
        \end{figure}

>>>>

    temperature than the GG.
    Also \(T_c\) of the RNG decreases

@@

    \subsubsection{Influence of the Average Degree on the Critical Temperature}
        One basic property of a graph is its average degree \(K\) -- sometimes
        called average \emph{coordination number}. \(K\) is defined as the mean count
        of neighbors per node.
        \begin{equation}
            K = \frac{1}{N} \sum_{\avg{i,j}} 1.
            \label{eq:degree}
        \end{equation}
        It is well known that the degree has an impact on the critical temperature.
        For example the Honeycomb lattice is of degree \(K=3\) and the
        respective critical temperature can be obtained by analytic means \cite{Wannier1945},
        yielding
        \begin{equation}
            \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52.
            \label{eq:exactHCTc}
        \end{equation}
        Note that this is lower than the critical temperature \(T_c = 2.269...\)
        characteristic for the square lattice with degree \(K=4\).\\
        This is plausible, because more edges lead to more neighbors.
        Consider, e.g., a fully polarized spin configuration. Now, the
        energy needed to flip a spin so that it assumes an orientation opposite
        to the orientation of its neighbors increases with the number of
        its neighbors. So the more edges are in
        the graph the more stable the system becomes with respect to spin flips
        at low \(T\), leading to an increasing value of \(T_c\).
        This is also an explanation why the \(T_c\) of the RNG is always
        lower than that of the GG: The degree of the RNG is lower.\\
        If one plots the degree of the graphs at different \(\sigma\) like
        in Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
        one recognizes that \(T_c\) and \(K\) are evidently correlated.
        The values for \(K\) are obtained as an average over \(100\)
        realizations of each graph type for \(L=16\) and \(L=32\) lattices.
        %~ Note that \(K\) is independent of \(L\) because of the periodic boundary.
        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        one can see that these curves are almost identical and the small
        errorbars suggest that they are sufficiently precise for this purpose.
        It seems reasonable to normalize \(T_c\) by the degree of the underlying
        graph. This is done in Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
        Indeed the normalization eliminates the jump and reduces the
        slope of the \(T_c\) curve for the GG. Hence it reduces differences
        between the RNG and the GG. However the elimination of the jump is
        unfortunately a coincidence and probably caused by a lucky choice of the
        function, which determines the coupling constants \(J\). As proof for
        this claim in Sec.\ \ref{appendix:fixedCoupling} the same analysis
        is performed for a model with fixed \(J\). There the jump gets narrower
        but is still existent. Anyway, the degree seems to have an impact on
        the critical temperature \(T_c\), but it is not a trivial one.
        Note that even after the normalization, the values of \(T_c / K\)
        for the RNG are smaller than those for the GG.
        \begin{figure}[htbp]
            \centering
            \subfigure[][]
            {
                \label{sfig:deg:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
            }
            \subfigure[][]
            {
                \label{sfig:deg:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_deg}
            }

@@

            \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
            {
                Top: Critical Temperature \(T_c\) of the graph over different
                disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.\\
                Bottom: Critical temperatures normalized by degree \(K\) over
                different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
                are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
                from Sec.\ \ref{sssec:J}.
            }
            \label{fig:Tc_deg_A0}
        \end{figure}\\
        Because Ref.\ \cite{Janke1994} gives for the DT with \(J=1\) a
        critical temperature \(T_{c,DT} = 3.80\), the obtained \(T_{c,GG} = 2.19\)
        and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should be very
        similar to a Poisson distributed set of nodes, can be compared.
        Note that while for the graph ensembles as mentioned in Sec. \ref{ssec:graphtypes}
        the relation \(DT \supseteq GG \supseteq RNG\) holds, also the
        relation \(T_{c,DT} \ge T_{c,GG} \ge T_{c,RNG}\) holds.
        Also keep in mind that the relation \(T_{c,GG} \ge T_{c,RNG}\)
        was true for \(\alpha = 0.5\) in the preceding sections.
        This phenomenon is also known from percolation where the relation
        \(p_{c,DT} \ge p_{c,GG} \ge p_{c,RNG}\) holds for the percolation
        threshold \(p_c\) -- the critical point of the percolation problem.
        That the subgraph hierachy can be translated to
        the sequence of \(p_c\) for the subgraphs, is known as the containment
        theorem \cite{fisher}.
        Possibly the containment theorem is also applicable on this kind of
        problem.
